A Closed-Form Solution to the Doppler Imaging Problem

### 2021-09-16 src/ms.tex
lots of updates

% \begin{figure}[t!]
%     \begin{centering}
%         \includegraphics[width=\linewidth]{figures/twospec.pdf}
%         \caption{%
%             An example of a star whose spectrum is different within the spot (\texttt{B}) and outside of the spot (\texttt{A}). 
%             Everywhere on the surface, the spectrum is a linear combination of two spectral components ($s_1$ and $s_2$).
%             As in Figure~\ref{fig:spot_y1bs}, we assume we do not know the map, the baseline, or either of the spectra.
%             The top row shows the true values for the map and the spectra, and the bottom row shows our inferred values. 
%         }
%         \label{fig:twospec}
%     \end{centering}
% \end{figure}

@@

\subsection{Dependence on inclination}
\label{sec:inc}
%
\begin{figure}[p!]
    \begin{centering}
        \includegraphics[width=0.98\linewidth]{figures/inclinations.pdf} % 
        \caption{%
            Recovered \texttt{STAR SPOT} map as a function of stellar inclination. 
            The observed spectra are continuum-normalized and the rest frame spectrum is assumed to be known exactly.
            In general, it is very difficult to infer features in the hemisphere facing away from the observer (in this case, the southern hemisphere). At low inclinations, those features are never in view, while at inclinations close to 90$^\circ$, it becomes difficult to differentiate between features above and below the equator.
        }
        \label{fig:inclinations}
    \end{centering}
\end{figure}
%
As in \citet{Vogt1987}, we also investigate the dependence of the solution on the inclination of the star.
Figure~\ref{fig:inclinations} shows the inferred map for the same problem setup as before (with SNR $\sim 100$), but this time varying the inclination between $10^\circ$ (nearly face-on) and $90^\circ$ (perfectly edge-on). 
As before, the inclination is assumed to be known exactly. 
We further keep the true equatorial velocity of the star constant across all panels, so that the figure corresponds to the same star viewed at different orientations. 
Because of this, decreasing the inclination decreases $v\sin i$, reducing the width of the convolution kernel and therefore the spatial resolution of our inferred map. 
Increasing the inclination does not result in appreciable changes until an inclination of $\sim 80^\circ$, above which it becomes difficult to differentiate between features in the northern and southern hemispheres, whose projected velocities are nearly equal. 
At $i = 90^\circ$, there is a formal degeneracy between the two hemispheres, which can be seen from the mirror-image symmetry in the inferred map. 
These results are broadly consistent with those of \citet{Vogt1987}.

>>>>

\begin{figure}[t!]
    \begin{centering}
        \includegraphics[width=0.39\linewidth]{figures/twospec_timeseries.pdf}
        \includegraphics[width=0.59\linewidth]{figures/twospec_maps.pdf}
        \includegraphics[width=\linewidth]{figures/twospec_spectra1.pdf}
        \includegraphics[width=\linewidth]{figures/twospec_spectra2.pdf}
        \caption{%
            An example of a star whose spectrum is different within the spot and outside of the spot.
        }
        \label{fig:twospec}
    \end{centering}
\end{figure}

@@

\subsection{Dependence on inclination}
\label{sec:inc}
%
\begin{figure}[p!]
    \begin{centering}
        \includegraphics[width=0.98\linewidth]{figures/inclinations.pdf} % 
        \caption{%
            Recovered \texttt{STAR SPOT} map as a function of stellar inclination. 
            The observed spectra are continuum-normalized and the rest frame spectrum is assumed to be known exactly.
            In general, it is very difficult to infer features in the hemisphere facing away from the observer (in this case, the southern hemisphere). At low inclinations, those features are never in view, while at inclinations close to 90$^\circ$, it becomes difficult to differentiate between features above and below the equator.
        }
        \label{fig:inclinations}
    \end{centering}
\end{figure}
%
As in \citet{Vogt1987}, we also investigate the dependence of the solution on the inclination of the star.
Figure~\ref{fig:inclinations} shows the inferred map for the same problem setup as before, but this time varying the inclination between $10^\circ$ (nearly face-on) and $90^\circ$ (perfectly edge-on). We also use a different surface map, this time with the word \texttt{STAR} in the northern hemisphere and the word \texttt{SPOT} in the southern hemisphere, to assess our ability to infer information across the entire stellar surface. \xxx{Given the added complexity of the map, we increase the spherical harmonic degree to} $l_\mathrm{max} = 20$, increase the SNR of our data to 200, and set the covariance of the spatial prior to $\boldsymbol{\Lambda}_\bvec{y} = 3\times 10^{-5}\bvec{I}$.
As before, the inclination is assumed to be known exactly. 
\xxx{We further keep the true equatorial velocity of the star constant} across all panels, so that the figure corresponds to the same star viewed at different orientations. 
Because of this, decreasing the inclination decreases $v\sin i$, reducing the width of the convolution kernel and therefore the spatial resolution of our inferred map. 
Increasing the inclination does not result in appreciable changes until an inclination of $\sim 80^\circ$, above which it becomes difficult to differentiate between features in the northern and southern hemispheres, whose projected velocities are nearly equal. 
At $i = 90^\circ$, there is a formal degeneracy between the two hemispheres, which can be seen from the mirror-image symmetry in the inferred map. 
These results are broadly consistent with those of \citet{Vogt1987}.
